An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-11-04 EconGrowth2.Rnw
Moved resample coefficient tables and 95% CI graphs to appendix.

Converting the resample data into 95\% confidence intervals 
provides data for Figure~\ref{fig:CD_Params_Graph}.
Appendix~\ref{sec:Model_Parameters} 
contains tables with numerical values of 
Cobb-Douglas model parameters and 95\% confidence intervals.

@@

Figure~\ref{fig:CDq_Cloud_Graph} shows ternary plots 
for $\alpha$, $\beta$, and $\gamma$ parameter values 
for Cobb-Douglas (with energy) resample models.

<<CDq_Cloud_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=ninePanelTernaryGraphHeight, fig.cap="Cobb-Douglas (with energy) resample model parameters.">>=
cdResampleTrianglePlot(energyType="Q")
@

@@

**** Include CES graphs here. Need to cover
all options: without energy and the three nesting
options. CIs? TBD which to include. ****

@@

@@

>>>>

@@

Figure~\ref{fig:CDq_Scatter_Graph} shows ternary plots 
for $\alpha$, $\beta$, and $\gamma$ parameter values 
for Cobb-Douglas (with energy) resample models.

<<CDq_Scatter_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=ninePanelTernaryGraphHeight, fig.cap="Cobb-Douglas (with energy) resample model parameters.">>=
cdResampleTrianglePlot(energyType="Q")
@

@@

Coefficients for each resampled CES model (without energy)
are shown in 
Figures~\ref{fig:CES_lambda_gamma_Scatter_Graph} and
\ref{fig:CES_sigma_1_delta_1_Scatter_Graph}. 
Note that the bottom of the vertical axis represents $\sigma = 0$.
The top of the vertical axis represents $\sigma = \infty$.
The crosshair on each graph shows the location 
of the fit to historical data. 
Dots are colored by whether or not the fitting routine
reports model convergence.

<<CES_lambda_gamma_Scatter_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (without energy) resample model parameters $\\lambda$ and $\\gamma$.">>=
cesResamplePlotLambdaGamma(energyType=NA)
@

<<CES_sigma_1_delta_1_Scatter_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (without energy) resample model parameters $\\sigma_1$ and $\\delta_1$.">>=
cesResamplePlotSigma_1Delta_1(energyType=NA)
@

@@

**** Matt: Remove $x$ and $u$ lines. Replace with lines for each nesting. ****

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{95\% Confidence Intervals}
\label{sec:Confidence_Intervals}
\setcounter{table}{0} % Restarts table number counter at 0 in this section.
\setcounter{figure}{0} % Restarts figure number counter at 0 in this section.
\setcounter{equation}{0} % Restarts equation counter to 0 in this section.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Resample coefficients in the scatter plots 
can be represented as 95\% confidence intervals 
by finding the parameter values associated with 
the middle 95\% of the data for each model parameter.
This appendix provides tables and graphs of the 95\% confidence
intervals on fitted model parameters.

%++++++++++++++++++++++++++++++
\subsection{Cobb-Douglas Models}
%++++++++++++++++++++++++++++++

The 95\% confidence intervals associated with Figure~\ref{fig:CD_Scatter_Graph} 
are shown in Table~\ref{tab:CD_Params_Table}.

<<CD_Params_Table, results='asis'>>=
printCDParamsTable(energyType=NA)    #Without energy
@

The data in Table~\ref{tab:CD_Params_Table} is plotted in
Figure~\ref{CD_Params_Graph}.

The 95\% confidence intervals associated with Figure~\ref{fig:CDq_Scatter_Graph} 
are shown in Table~\ref{tab:CDq_Params_Table}
and Figure~\ref{CDq_Params_Graph}.

<<CDq_Params_Table, results='asis'>>=
printCDParamsTable(energyType="Q")   #With energy
@

<<CDq_Params_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=cdParameterGraphHeight, fig.cap="Cobb-Douglas (with energy) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
createCDParamsGraph(energyType="Q")
@

%++++++++++++++++++++++++++++++
\subsection{CES Models}
%++++++++++++++++++++++++++++++

The 95\% confidence intervals associated with Figure~\ref{fig:}
are shown in Table~\ref{tab:} and Figure~\ref{fig:}
**** Ensure that we have tables for all nestings. ****

<<CES_Params_Table, results='asis'>>=
printCESParamsTableA(energyType=NA)
printCESParamsTableB(energyType=NA)
@

The 95\% confidence intervals associated with Figure~\ref{fig:}
are shown in Table~\ref{tab:} and Figure~\ref{fig:}
**** Ensure that we have figures for all nestings. ****

<<CES_Params_Graph, fig.pos="H", fig.width=cesParameterGraphWidth, fig.height=cesParameterGraphHeight, fig.cap="CES (without energy) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
createCESParamsGraph(energyType=NA)
@

The 95\% confidence intervals associated with Figure~\ref{fig:}
are shown in Table~\ref{tab:} and Figure~\ref{fig:}
**** Ensure that we have tables for all nestings. ****

<<CESq_Params_Table, results='asis'>>=
printCESParamsTableA(energyType="Q")
printCESParamsTableB(energyType="Q")
@

The 95\% confidence intervals associated with Figure~\ref{fig:}
are shown in Table~\ref{tab:} and Figure~\ref{fig:}
**** Ensure that we have figures for all nestings. ****

<<CESq_Params_Graph, fig.pos="H", fig.width=cesParameterGraphWidth, fig.height=cesParameterGraphHeight, fig.cap="CES (with energy, ($kl$)$e$ nesting) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
createCESParamsGraph(energyType="Q")
@

%++++++++++++++++++++++++++++++
\subsection{LINEX Model}
%++++++++++++++++++++++++++++++

The 95\% confidence intervals associated with Figure~\ref{fig:}
are shown in Table~\ref{tab:} and Figure~\ref{fig:}
**** Ensure that we have figures for all nestings. ****

<<LINEX_Params_Table, results='asis'>>=
printLINEXParamsTable(energyType="Q")
@

<<LINEXq_Params_Graph, fig.pos="H", fig.width=linexParameterGraphWidth, fig.height=linexParameterGraphHeight, fig.cap="LINEX model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
createLINEXParamsGraph(energyType="Q")
@
